\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools,bm}
\usepackage{booktabs,array,multirow}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{caption}
\usepackage[T1]{fontenc}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\setcitestyle{authoryear,round,semicolon}
\doublespacing
\setlength{\parindent}{2em}
\setlength{\parskip}{0pt}
\captionsetup{font=small,labelfont=bf,labelsep=period}

\renewcommand{\thesection}{\Roman{section}}
\renewcommand{\thesubsection}{\Alph{subsection}}
\titleformat{\section}[block]
  {\centering\normalsize\bfseries}
  {\thesection.}
  {0.5em}
  {\MakeUppercase}
\titlespacing*{\section}{0pt}{2.0ex plus .5ex minus .2ex}{1.2ex}
\titleformat{\subsection}[block]
  {\normalsize\bfseries}
  {\thesubsection.}
  {0.5em}
  {}
\titlespacing*{\subsection}{0pt}{1.5ex plus .4ex minus .2ex}{0.7ex}

\setlength{\emergencystretch}{3em}
\hbadness=10000
\vbadness=10000
\hfuzz=100pt
\vfuzz=100pt
\raggedbottom

\newtheorem{assumption}{Assumption}
\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}

\newcommand{\E}{\mathbb{E}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\1}{\mathbf{1}}
\newcommand{\dd}{\,\mathrm{d}}
\newcommand{\argmax}{\operatorname*{arg\,max}}
\newcommand{\Inew}{\mathcal{N}}
\newcommand{\Surp}{\mathcal{S}}
\newcommand{\Tset}{\mathcal{T}}
\newcommand{\Lbar}{\bar L}

\title{Institutional Reform and Pharmaceutical Innovation
\\An Analysis Based on the MAH System}
\author{Danni Yangchen, Wenxiao Dong, Xinhao Wang}
\date{}

\begin{document}
\maketitle

\begin{abstract}
We develop a dynamic industry model to study how China's Marketing Authorization Holder (MAH) reform changes firm boundaries, organizational transitions, and the number of new original-drug products commercialized in the pharmaceutical industry. We model two medicine categories: generic drugs and original drugs. Integrated firms can produce both medicines and conduct original-drug research. Manufacturing-specialized firms can produce both medicines but do not originate new original-drug ideas. Research-specialized firms generate original-drug ideas only. Before MAH, research-specialized firms cannot independently commercialize original-drug ideas through external production; after MAH, they can retain authorization while outsourcing manufacturing to qualified producers. We build the model on a Hopenhayn-style stationary industry shell with endogenous entry and exit, convex innovation effort for original-drug discovery, and a contract-manufacturing market for MAH-enabled commercialization. The equilibrium delivers predictions for incumbent transition matrices, entry composition, producer-side outcomes, and the number of new original-drug products.
\end{abstract}

\section{Introduction and literature strategy}

We study whether MAH relaxes the institutional bundle between original-drug R\&D and production capacity, thereby changing organizational boundaries and increasing the number of new original-drug products that reach commercialization in China's pharmaceutical industry. We focus on the pharmaceutical industry rather than the whole economy. Accordingly, the surplus object that we define below is a pharmaceutical-industry surplus object rather than a whole-economy welfare object.

We organize the model around five literature blocks. First, we use a stationary heterogeneous-firm industry shell with endogenous entry, endogenous exit, and invariant distributions following \citet{Hopenhayn1992}. This block also connects to the selection logic in \citet{Jovanovic1982}, the dynamic-industry control language in \citet{EricsonPakes1995}, and the equilibrium-composition perspective in \citet{Luttmer2007}. Second, we use the innovation literature to justify firm-level original-drug research effort and composition effects on industry outcomes, following \citet{KletteKortum2004} and \citet{AkcigitKerr2018}. Third, we use the market-for-technology and market-for-ideas literatures to motivate why innovative firms need not be vertically integrated in order to create value, following \citet{AroraFosfuriGambardella2001}, \citet{AroraMerges2004}, \citet{GansStern2000}, \citet{GansStern2003}, and \citet{GansHsuStern2008}. Fourth, we use pharmaceutical-policy and pharmaceutical-organization references to motivate why regulatory design can change commercialization and innovation without operating only through prices, following \citet{Lakdawalla2018}, \citet{ChandraEtAl2026}, and \citet{JiaMaYangZhang2023}. Fifth, we borrow only the distinction between invention and implementation from recent startup-innovation work, following \citet{FonsRosenRoldanBlancoSchmitz2026}; we do not borrow their acquisition, search, or bargaining layers.

This modeling strategy matches our empirical question. MAH is not a merger policy, and our data do not identify bargaining primitives. We therefore need an upstream original-drug idea-generation margin, a downstream commercialization margin, a contract-manufacturing market, and organizational switching across integrated, research-specialized, and manufacturing-specialized firms. We do not need an acquisition block or a full incomplete-contract model.

\subsection{What we borrow and what we change}

We borrow the value-function logic, free-entry condition, and stationary distribution from \citet{Hopenhayn1992}, but we replace a single firm type with three organizational states because our question is about firm boundaries. We borrow convex innovation effort from \citet{KletteKortum2004}, but we apply it only to original-drug idea generation rather than to generic-product expansion. We borrow the composition logic from \citet{AkcigitKerr2018}, but we apply it to a sectoral reorganization problem rather than to long-run growth accounting. We borrow commercialization and specialization logic from \citet{AroraMerges2004} and \citet{GansStern2003}, but we translate them into an MAH-specific outsourcing environment. Finally, we borrow the invention-versus-implementation distinction from \citet{FonsRosenRoldanBlancoSchmitz2026}, but we replace startup acquisition with MAH-enabled commercialization through qualified external manufacturing.

These changes are substantive rather than cosmetic. They make the model fit China's pharmaceutical industry and the MAH institution while preserving the literature's core mechanisms.

\section{Institutional background and identification boundary}

We model China's pharmaceutical industry as an environment with two medicine categories,
\[
k \in \{G,O\},
\]
where $G$ denotes generic drugs and $O$ denotes original drugs. We use this distinction because our policy question is about \emph{new original-drug products}, not total pharmaceutical output. Generic production provides cash flow and manufacturing demand, but MAH mainly changes the commercialization environment for original-drug ideas.

Let $M\in\{0,1\}$ denote the regulatory regime. We interpret $M=0$ as the pre-MAH regime and $M=1$ as the post-MAH regime. We model MAH through two reduced-form channels,
\begin{align}
\tau_M(1) &< \tau_M(0), \label{eq:tauM}\\
\kappa_{sj}(1) &\le \kappa_{sj}(0)
\qquad \text{for } s,j\in\{A,B,C\},\ s\neq j.
\label{eq:kappaM}
\end{align}
Here $\tau_M(M)$ is the commercialization friction faced especially by research-specialized firms and $\kappa_{sj}(M)$ is the cost of reorganizing from organizational type $s$ to organizational type $j$.

Our key MAH restriction is not that all firms suddenly invent more after reform. Rather, MAH changes whether a research-specialized firm can retain authorization and commercialize an original-drug idea through external production. In the benchmark below, that restriction appears as a pre-MAH collapse of the commercialization-success probability for type-$B$ firms. This is how we encode the institutional point that before MAH, the firms that could both research and produce were the only firms able to bring new original drugs to market independently.

We also keep the identification boundary explicit. With outcome data alone, we can identify whether MAH raises the number of new original-drug products. We cannot claim to directly estimate the commercialization probability itself from those data alone. We therefore use the commercialization block as a structural interpretation, and we reinforce it with transition evidence, entry evidence, and commercialization proxies.

\section{Environment, dimensions, and notation}

Time is discrete, $t=0,1,2,\dots$. There are three active firm types,
\[
\Tset = \{A,B,C\},
\]
where:
\begin{itemize}[leftmargin=2em]
    \item $A$ denotes integrated firms that can produce generic drugs, produce original drugs, and conduct original-drug R\&D;
    \item $B$ denotes research-specialized firms that generate ideas for new original drugs only;
    \item $C$ denotes manufacturing-specialized firms that can produce generic and original drugs but do not originate new original-drug ideas.
\end{itemize}
There is also a pool of potential entrants.

Each active firm has a one-dimensional idiosyncratic capability state $z\in Z\subset\R_+$, where $Z$ is compact. We adopt a one-state benchmark because this is the safest baseline relative to the heterogeneous-firm literature following \citet{Hopenhayn1992} and \citet{Jovanovic1982}. We interpret $z$ broadly as the capability state that affects research productivity, commercialization ability, organizational adaptation, and manufacturing efficiency. We let the three organizational forms load differently on the same state rather than introducing multiple latent capability processes that our current empirical design does not separately identify.

There are two endogenous prices,
\[
\begin{aligned}
w &\quad \text{(industry wage or composite factor price)},\\
p_m &\quad \text{(price of qualified contract-manufacturing services)}.
\end{aligned}
\]
We determine both in stationary equilibrium. The price $p_m$ summarizes the scarcity of qualified external production and therefore directly affects MAH-enabled commercialization.

\subsection{Why we use optimized flow payoffs rather than explicit capital and labor in every Bellman equation}

This is standard in the literature we borrow from. \citet{Hopenhayn1992} writes firm values in terms of optimized current profit rather than a separate capital and labor block inside every Bellman equation. \citet{EricsonPakes1995} also write the dynamic problem around firm values and controlled state transitions rather than around a full static cost-minimization problem in every period. \citet{KletteKortum2004} similarly summarize production-side detail inside firm-level value and innovation objects. We follow that practice. When we need labor-market closure, we recover labor demand from type-specific optimized flow payoffs rather than solving a separate static factor-allocation problem inside every type block.

\subsection{Main notation}

Table \ref{tab:notation} defines the main objects.

\clearpage

\begin{table}[htbp]
\centering
\caption{Main notation}
\label{tab:notation}
\footnotesize
\begin{tabular}{p{0.24\textwidth}p{0.68\textwidth}}
\toprule
Symbol & Definition \\
\midrule
$M$ & Policy regime: $M=0$ pre-MAH, $M=1$ post-MAH. \\
$k\in\{G,O\}$ & Product category: generic $(G)$ or original $(O)$. \\
$z$ & Firm capability state. \\
$w$ & Industry wage or composite factor price. \\
$p_m$ & Price of qualified contract-manufacturing services. \\
$\tau_M(M)$ & Commercialization friction faced by type-$B$ firms. \\
$\kappa_{sj}(M)$ & Switching cost from organizational type $s$ to organizational type $j$. \\
$V_s(z;M)$ & Value of operating as type $s\in\{A,B,C\}$ at state $z$. \\
$\Pi_A(z;w,M)$ & Optimized current operating payoff of an integrated firm. \\
$\Pi_B(z;p_m,M)$ & Optimized current operating payoff of a research-specialized firm. \\
$\Pi_C(z;p_m,w,M)$ & Optimized current operating payoff of a manufacturing-specialized firm. \\
$x_A$ & Original-drug idea-generation intensity chosen by type-$A$ firms. \\
$x_B$ & Original-drug idea-generation intensity chosen by type-$B$ firms. \\
$m$ & Qualified contract-manufacturing output chosen by type-$C$ firms for MAH-enabled original drugs. \\
$\pi_A^G,\pi_C^G$ & Generic-drug operating profits for types $A$ and $C$. \\
$\pi_A^{O,\mathrm{inc}},\pi_C^{O,\mathrm{inc}}$ & Incumbent operating profits from already commercialized original drugs for types $A$ and $C$. \\
$R_A(z)$ & Gross private value of one successfully commercialized original-drug idea inside type $A$. \\
$R_B(z)$ & Gross private value of one successfully commercialized original-drug idea for type $B$. \\
$\lambda_A(z)$ & Commercialization-success rate of an original-drug idea inside type $A$. \\
$\lambda_B(z,p_m,M)$ & Commercialization-success rate of an original-drug idea generated by type $B$ and commercialized through qualified external manufacturing. \\
$Q_j(\cdot\mid z,M)$ & Transition kernel for next period's capability state when the current-period organizational choice is $j$. \\
$G$ & Distribution of entrants' initial capability draws. \\
$c_{Ej}$ & Entry cost for entering as type $j$. \\
$\mu_j$ & Stationary measure of incumbent firms of type $j$. \\
$P_{sj}(M)$ & Model-implied transition probability from current type $s$ to chosen type $j$ in the stationary distribution. \\
$\mathbf P(M)$ & Stationary incumbent transition matrix under regime $M$. \\
$\mathbf e(M)$ & Entry-composition vector under regime $M$. \\
$\Inew(M)$ & Number of new original-drug products commercialized in the industry. \\
$\Surp(M)$ & Pharmaceutical-industry surplus under regime $M$. \\
\bottomrule
\end{tabular}
\end{table}

\section{Timing within a period}

We adapt the timing from dynamic industry models such as \citet{EricsonPakes1995}, while keeping the stationary entry-and-exit shell of \citet{Hopenhayn1992}. We choose current-period organization before current-period operating choices because MAH changes the same-period feasibility of outsourcing versus internal commercialization.

Within each period, events occur in the following order.
\begin{enumerate}[leftmargin=2em]
    \item A firm enters the period with current organizational type $s\in\{A,B,C\}$ and current capability $z$.
    \item The firm chooses its current-period organizational form $j\in\mathcal J(s)$, where the feasible set allows it to remain in its current form, switch to either of the other two forms, or exit. If $j\neq s$, the firm pays switching cost $\kappa_{sj}(M)$ immediately.
    \item Conditional on the chosen current-period organizational form $j$, the firm chooses current operating controls and earns current operating payoff $\Pi_j$.
    \item If the firm does not exit, next period's capability state is drawn from $Q_j(\dd z'\mid z,M)$.
    \item Potential entrants draw initial capability from $G$ and choose whether to enter as type $A$, $B$, or $C$.
\end{enumerate}

This timing is the cleanest way to keep the MAH outsourcing margin and the organizational-boundary margin inside the same-period problem. It also lets us write the value functions in the standard current-flow-plus-continuation form.

\section{Static operating payoffs with two medicines}

\subsection{Integrated firms}

Following \citet{KletteKortum2004}, adapted to a two-medicine pharmaceutical environment, we let an integrated firm choose original-drug idea-generation intensity $x_A\ge 0$. Type $A$ earns cash flow from producing generic drugs, cash flow from already commercialized original drugs, and option value from generating new original-drug ideas. Its current-period payoff is
\begin{equation}
\pi_A(z;w,M)
=
\pi_A^G(z;w)
+\pi_A^{O,\mathrm{inc}}(z;w,M)
-f_A
+x_A\Omega_A(z)-\frac{\chi_A}{\eta}x_A^{\eta},
\qquad \eta>1,
\label{eq:piA}
\end{equation}
where $\Omega_A(z)\equiv \lambda_A(z)R_A(z)$ is the expected marginal value of a new original-drug idea inside an integrated firm.

The first-order condition gives
\begin{equation}
x_A^*(z)=\left(\frac{\Omega_A(z)}{\chi_A}\right)^{\frac{1}{\eta-1}},
\label{eq:xA}
\end{equation}
and the optimized current payoff is
\begin{equation}
\Pi_A(z;w,M)
=
\pi_A^G(z;w)
+\pi_A^{O,\mathrm{inc}}(z;w,M)
-f_A
+
\frac{\eta-1}{\eta}\chi_A^{-\frac{1}{\eta-1}}\Omega_A(z)^{\frac{\eta}{\eta-1}}.
\label{eq:PiA}
\end{equation}

Equation \eqref{eq:PiA} adapts the innovation-intensity block in \citet{KletteKortum2004} to the MAH setting. The main change is that integrated firms earn profits from both medicines, while their innovative effort is directed only to new original drugs.

\subsection{Research-specialized firms}

Following \citet{KletteKortum2004} for convex innovative effort and adapting the commercialization block using the market-for-ideas logic of \citet{GansStern2003} and the invention-versus-implementation distinction emphasized by \citet{FonsRosenRoldanBlancoSchmitz2026}, we let a research-specialized firm choose original-drug idea-generation intensity $x_B\ge 0$. Unlike earlier drafts, we do not let the research firm choose a separate implementation intensity as a top-level control. Instead, commercialization through qualified external manufacturing is summarized by a reduced-form success rate.

The expected payoff from one original-drug idea is
\begin{equation}
H_B(z;p_m,M)=\lambda_B(z,p_m,M)\bigl(R_B(z)-p_m\bigr)-\tau_M(M),
\label{eq:HB}
\end{equation}
where $R_B(z)$ is the gross private value of a successfully commercialized original-drug idea and $\lambda_B(z,p_m,M)\in[0,1]$ is the probability that the idea is successfully commercialized through qualified external manufacturing.

We assume
\begin{equation}
\frac{\partial \lambda_B}{\partial z}>0,
\qquad
\frac{\partial \lambda_B}{\partial p_m}<0,
\qquad
\frac{\partial \lambda_B}{\partial M}\ge 0.
\label{eq:lambda_monotone}
\end{equation}
The first inequality says more capable research firms are better at turning ideas into commercializable products. The second says scarce or expensive manufacturing capacity makes commercialization harder. The weak inequality in $M$ allows MAH to improve commercialization directly, in addition to lowering the friction $\tau_M(M)$.

To encode the institutional restriction that before MAH, a research-specialized firm could not independently commercialize a new original-drug idea through external production while retaining the relevant rights, we impose the benchmark assumption
\begin{equation}
\lambda_B(z,p_m,0)=0
\qquad \text{for all } z\in Z.
\label{eq:premah_zero}
\end{equation}
After MAH, that restriction is relaxed, so for a nondegenerate subset of states,
\begin{equation}
\lambda_B(z,p_m,1)>0.
\label{eq:postmah_positive}
\end{equation}

The current-period payoff of a type-$B$ firm is
\begin{equation}
\pi_B(z;p_m,M)
=
-f_B+x_B H_B(z;p_m,M)-\frac{\chi_B}{\eta}x_B^{\eta}.
\label{eq:piB}
\end{equation}
Define $[a]_+=\max\{a,0\}$. Then
\begin{equation}
x_B^*(z;p_m,M)=\left(\frac{[H_B(z;p_m,M)]_+}{\chi_B}\right)^{\frac{1}{\eta-1}},
\label{eq:xB}
\end{equation}
and the optimized current payoff is
\begin{equation}
\Pi_B(z;p_m,M)
=
-f_B+
\frac{\eta-1}{\eta}\chi_B^{-\frac{1}{\eta-1}}[H_B(z;p_m,M)]_+^{\frac{\eta}{\eta-1}}.
\label{eq:PiB}
\end{equation}

Equations \eqref{eq:HB}--\eqref{eq:PiB} are the key MAH adaptation. We preserve the invention-versus-implementation distinction, but we implement it in a way that fits the reality of China's pharmaceutical industry: research-specialized firms generate original-drug ideas, while commercialization depends on whether MAH lets them access qualified external manufacturing.

\subsection{Manufacturing-specialized firms}

Following the static-profit logic in \citet{Hopenhayn1992}, we let a manufacturing-specialized firm earn profits from producing generic drugs and from producing already commercialized original drugs, while also choosing the amount of qualified contract manufacturing dedicated to MAH-enabled original-drug commercialization. Its current-period payoff is
\begin{equation}
\pi_C(z;p_m,w,M)
=
\pi_C^G(z;w)
+\pi_C^{O,\mathrm{inc}}(z;w,M)
-f_C
+\max_{m\ge 0}\left\{p_m m-c(m,z;w)\right\},
\label{eq:piC}
\end{equation}
where $c_m>0$, $c_{mm}>0$, and $c_z<0$. The optimized current payoff is
\begin{equation}
\Pi_C(z;p_m,w,M)
=
\pi_C^G(z;w)
+\pi_C^{O,\mathrm{inc}}(z;w,M)
-f_C
+\max_{m\ge 0}\left\{p_m m-c(m,z;w)\right\}.
\label{eq:PiC}
\end{equation}

The important modeling point is that type $C$ can produce both medicines, but it does not originate new original-drug ideas. That is exactly why MAH changes the interaction between type $B$ and type $C$ without making type $C$ itself an innovator.

\section{Dynamic organizational choice and value functions}

Following \citet{Hopenhayn1992}, we write firm values as current flow payoff plus discounted continuation value. Following \citet{EricsonPakes1995}, we let organizational form be a dynamic control. The feasible current-period choice sets are
\begin{align}
\mathcal J(A)&=\{A,B,C,\text{exit}\}, \\
\mathcal J(B)&=\{A,B,C,\text{exit}\}, \\
\mathcal J(C)&=\{A,B,C,\text{exit}\}.
\end{align}
We set $\kappa_{ss}(M)=0$ for $s\in\{A,B,C\}$.

For each current type $s$ and chosen current-period type $j$, we define the choice-specific value as
\begin{equation}
W_{sj}(z;M)=\Pi_j(z;w,p_m,M)-\kappa_{sj}(M)+\beta\int V_j(z';M)Q_j(\dd z'\mid z,M),
\label{eq:choice_specific_value}
\end{equation}
with the convention $W_{s,\text{exit}}(z;M)=0$.

Equation \eqref{eq:choice_specific_value} is our direct adaptation of the incumbent value-function logic in \citet{Hopenhayn1992} and the dynamic-control logic in \citet{EricsonPakes1995}. The substantive change is that we let the firm choose among three organizational forms and we let current-period organization determine current-period commercialization possibilities.

The incumbent Bellman equations are then
\begin{align}
V_A(z;M) &= \max\bigl\{W_{AA}(z;M),W_{AB}(z;M),W_{AC}(z;M),0\bigr\}, \label{eq:VA}\\
V_B(z;M) &= \max\bigl\{W_{BA}(z;M),W_{BB}(z;M),W_{BC}(z;M),0\bigr\}, \label{eq:VB}\\
V_C(z;M) &= \max\bigl\{W_{CA}(z;M),W_{CB}(z;M),W_{CC}(z;M),0\bigr\}. \label{eq:VC}
\end{align}

We keep all six pairwise organizational switches in the baseline because the transition matrix is a first-order empirical object in the paper. At the same time, we expect some direct switches -- especially $B\rightarrow C$ and $C\rightarrow B$ -- to be empirically rare. In calibration, the corresponding switching costs can become large if the data say these moves almost never happen.

\subsection{Choice regions and the transition matrix}

Because the organizational choice is deterministic in the benchmark, the model generates a transition matrix through stationary choice regions rather than through exogenous logit shocks. For each current type $s$ and chosen type $j\in\{A,B,C,\text{exit}\}$, define
\begin{equation}
\mathcal Z_{sj}(M)=\left\{z\in Z: j \text{ solves the Bellman problem for a current type-}s\text{ firm at state } z\right\}.
\label{eq:choice_region}
\end{equation}

Let $\mu_s$ denote the stationary measure of firms whose current type is $s$. Then the model-implied incumbent transition probability from $s$ to $j$ is
\begin{equation}
P_{sj}(M)=\frac{\mu_s\bigl(\mathcal Z_{sj}(M)\bigr)}{\mu_s(Z)}.
\label{eq:transition_prob}
\end{equation}
The incumbent transition matrix is therefore
\begin{equation}
\mathbf P(M)=
\begin{pmatrix}
P_{AA}(M) & P_{AB}(M) & P_{AC}(M) & P_{A,\mathrm{exit}}(M) \\
P_{BA}(M) & P_{BB}(M) & P_{BC}(M) & P_{B,\mathrm{exit}}(M) \\
P_{CA}(M) & P_{CB}(M) & P_{CC}(M) & P_{C,\mathrm{exit}}(M)
\end{pmatrix},
\label{eq:transition_matrix}
\end{equation}
where each row sums to one. Equation \eqref{eq:transition_matrix} is the exact theoretical counterpart of the pre/post transition matrix that we plan to estimate from the firm-level panel.

\section{Entry}

Following the free-entry logic of \citet{Hopenhayn1992}, we let potential entrants draw an initial capability $z_0$ from distribution $G$ and choose whether to enter as type $A$, $B$, or $C$. We define entrant values as
\begin{align}
\bar V_E^A(M)&=\int V_A(z_0;M)G(\dd z_0)-c_{EA}, \\
\bar V_E^B(M)&=\int V_B(z_0;M)G(\dd z_0)-c_{EB}, \\
\bar V_E^C(M)&=\int V_C(z_0;M)G(\dd z_0)-c_{EC}.
\end{align}

Let $n_E^A(M),n_E^B(M),n_E^C(M)$ denote entrant masses. Free entry implies
\begin{align}
\bar V_E^A(M) &\le 0, & n_E^A(M)>0 &\implies \bar V_E^A(M)=0, \\
\bar V_E^B(M) &\le 0, & n_E^B(M)>0 &\implies \bar V_E^B(M)=0, \\
\bar V_E^C(M) &\le 0, & n_E^C(M)>0 &\implies \bar V_E^C(M)=0.
\end{align}

This entry block separates entrant composition from incumbent reorganization. The entrant-composition vector is
\begin{equation}
\mathbf e(M)=\bigl(e_A(M),e_B(M),e_C(M)\bigr),
\qquad
e_j(M)=\frac{n_E^j(M)}{n_E^A(M)+n_E^B(M)+n_E^C(M)}.
\label{eq:entry_vector}
\end{equation}

Equations \eqref{eq:transition_matrix} and \eqref{eq:entry_vector} are different empirical objects. The first describes incumbent reorganization and exit. The second describes which organizational forms new firms choose at entry. We must measure both in the data.

\paragraph{Optional extension.}
If later evidence strongly supports an external-finance or entry-support channel, we can introduce a reduced-form term $\phi_B(M)$ and write
\begin{equation}
\bar V_E^B(M)=\int V_B(z_0;M)G(\dd z_0)-c_{EB}+\phi_B(M),
\qquad
\phi_B(1)\ge \phi_B(0).
\end{equation}
We do not include this block in the benchmark because the current empirical design does not require it.

\section{Market clearing and stationary equilibrium}

\subsection{Qualified contract-manufacturing market}

The qualified contract-manufacturing market is the minimal extra equilibrium block needed for the MAH mechanism. Total demand is
\begin{equation}
D_m(p_m,M)=\int x_B^*(z;p_m,M)\,\lambda_B(z,p_m,M)\,\mu_B(\dd z),
\label{eq:Dm}
\end{equation}
while total supply is
\begin{equation}
S_m(p_m,w)=\int m^*(z;p_m,w)\,\mu_C(\dd z),
\label{eq:Sm}
\end{equation}
where $m^*(z;p_m,w)$ is the optimizer in equation \eqref{eq:PiC}. Market clearing requires
\begin{equation}
D_m(p_m,M)=S_m(p_m,w).
\label{eq:pm_clear}
\end{equation}

\subsection{Labor market}

We close the pharmaceutical-industry equilibrium with a simple labor market. Let labor demand by each type be $\ell_A(z;w)$, $\ell_B(z;p_m,M)$, and $\ell_C(z;p_m,w)$. Then aggregate labor demand is
\begin{equation}
\begin{aligned}
L_D(M)={}&\int \ell_A(z;w)\mu_A(\dd z)+\int \ell_B(z;p_m,M)\mu_B(\dd z)\\
&+\int \ell_C(z;p_m,w)\mu_C(\dd z)+\sum_{j\in\{A,B,C\}}\ell_E^j n_E^j(M),
\end{aligned}
\label{eq:labor_demand}
\end{equation}
where $\ell_E^j$ is setup labor for entrants of type $j$. Market clearing requires
\begin{equation}
L_D(M)=\Lbar.
\label{eq:labor_clear}
\end{equation}

\subsection{Stationary distribution}

For any measurable set $B\subseteq Z$, the next-period measure of type $j$ firms is
\begin{equation}
\mu'_j(B)
=
\sum_{s\in\{A,B,C\}}\int \1\{g_s(z;M)=j\}\,Q_j(B\mid z,M)\,\mu_s(\dd z)
+n_E^j(M)G(B),
\qquad j\in\{A,B,C\},
\label{eq:stationary_measure}
\end{equation}
where $g_s(z;M)$ is the optimal organizational policy. A stationary equilibrium requires $\mu'_j=\mu_j$ for each $j$.

\begin{definition}[Stationary competitive equilibrium]
For a given regime $M$, a stationary equilibrium consists of value functions $\{V_A,V_B,V_C\}$, operating policy rules $\{x_A^*,x_B^*,m^*\}$, organizational policy rules $\{g_A,g_B,g_C\}$, stationary measures $\{\mu_A,\mu_B,\mu_C\}$, entrant masses $\{n_E^A,n_E^B,n_E^C\}$, and prices $(w,p_m)$ such that:
\begin{enumerate}[leftmargin=2em]
    \item incumbent firms solve the Bellman system in equations \eqref{eq:VA}--\eqref{eq:VC},
    \item entrants satisfy the free-entry conditions,
    \item the qualified contract-manufacturing market clears,
    \item the labor market clears,
    \item the stationary measures are invariant under the optimal policy rules and entrant masses.
\end{enumerate}
\end{definition}

\section{New original-drug products, producer-side outcomes, and pharmaceutical-industry surplus}

The object of interest is not total pharmaceutical output. It is the number of \emph{new original-drug products} commercialized. We define
\begin{equation}
\Inew(M)=
\int \lambda_A(z)x_A^*(z)\mu_A(\dd z)
+
\int \lambda_B(z,p_m,M)x_B^*(z;p_m,M)\mu_B(\dd z).
\label{eq:Inew}
\end{equation}
Equation \eqref{eq:Inew} says that new original-drug products come from two sources: integrated firms' in-house research and commercialization, and research-specialized firms' post-MAH commercialization through qualified external production. This is the main policy object in the paper.

To connect the model more closely to producer-side evidence in China's pharmaceutical industry, we define the average current payoff of manufacturing-specialized firms as
\begin{equation}
\bar\Pi_C(M)=\frac{\int \Pi_C(z;p_m,w,M)\mu_C(\dd z)}{\int \mu_C(\dd z)}.
\end{equation}

We define a pharmaceutical-industry surplus object,
\begin{equation}
\begin{aligned}
\Surp(M)={}&CS^{\mathrm{pharma}}(M)+\int \Pi_A(z;w,M)\mu_A(\dd z)\\
&+\int \Pi_B(z;p_m,M)\mu_B(\dd z)+\int \Pi_C(z;p_m,w,M)\mu_C(\dd z)-SC(M),
\end{aligned}
\label{eq:industry_surplus}
\end{equation}
where $CS^{\mathrm{pharma}}(M)$ is consumer surplus in the pharmaceutical industry and $SC(M)$ collects organizational switching and reorganization costs. This is an industry object, not a whole-economy welfare measure.

\section{Assumptions and comparative statics}

\begin{assumption}[Regularity]
$Z$ is compact. The transition kernels $Q_j(\cdot\mid z,M)$ are weakly continuous in $z$. Flow-payoff functions are bounded and continuous in their arguments.
\end{assumption}

\begin{assumption}[Convexity]
$\eta>1$, $c_m>0$, and $c_{mm}>0$. The innovation blocks and the manufacturing block are well behaved.
\end{assumption}

\begin{assumption}[Policy effect]
MAH strictly lowers the commercialization friction and weakly lowers selected switching costs:
\[
\tau_M(1)<\tau_M(0),
\qquad
\kappa_{sj}(1)\le \kappa_{sj}(0)
\text{ for } s,j\in\{A,B,C\},\ s\neq j.
\]
\end{assumption}

\begin{proposition}[MAH raises the value of research specialization]
Suppose Assumptions 1--3 hold. Then for any state $z$ such that post-MAH outsourced commercialization is feasible, a fall in $\tau_M$ or a rise in $\lambda_B(z,p_m,M)$ raises $H_B(z;p_m,M)$ weakly, raises $x_B^*(z;p_m,M)$ weakly, and raises the choice-specific value $W_{sB}(z;M)$ for every current type $s$.
\end{proposition}

\begin{proof}
Equation \eqref{eq:HB} implies that a fall in $\tau_M$ or a rise in $\lambda_B$ raises the one-idea value pointwise. Equation \eqref{eq:xB} then implies that research effort rises weakly. Equation \eqref{eq:PiB} implies that the optimized current payoff of operating as a research-specialized firm rises weakly. Finally, equation \eqref{eq:choice_specific_value} implies that the value of choosing type $B$ rises weakly.
\end{proof}

\begin{proposition}[MAH changes the transition matrix]
If MAH lowers selected switching costs and raises the value of operating as type $B$, then the post-MAH incumbent transition matrix $\mathbf P(1)$ differs from the pre-MAH matrix $\mathbf P(0)$. In particular, the rows associated with current types $A$ and $B$ shift toward type $B$ whenever the direct gain from research specialization dominates the induced wage and manufacturing-price feedbacks.
\end{proposition}

\begin{proof}
Lower switching costs and a higher type-$B$ operating payoff expand the choice regions $\mathcal Z_{AB}(M)$ and $\mathcal Z_{BB}(M)$ unless equilibrium price feedbacks fully offset the direct effect. Since transition probabilities are generated by these regions through equation \eqref{eq:transition_prob}, the transition matrix changes.
\end{proof}

\begin{proposition}[MAH increases the number of new original-drug products]
Suppose MAH raises the entrant value of type $B$ and qualified contract-manufacturing supply is sufficiently elastic near the stationary equilibrium. Then entry composition shifts toward research-specialized firms, qualified contract-manufacturing demand rises, and the number of new original-drug products in equation \eqref{eq:Inew} rises whenever the increase in research-specialized idea generation dominates any decline in integrated-firm original-drug effort.
\end{proposition}

\begin{proof}
The free-entry condition implies that a higher expected entrant value for type $B$ expands type-$B$ entry until entry rents are dissipated or until the relevant corner is reached. A larger mass of profitable type-$B$ ideas raises demand for qualified contract manufacturing through equation \eqref{eq:Dm}. Equation \eqref{eq:Inew} then shows that the sign is governed by the net composition effect between integrated and research-specialized original-drug innovation.
\end{proof}

\begin{proposition}[Producer-side outcomes and industry surplus need not move one-for-one with new products]
A rise in the number of new original-drug products after MAH does not imply a rise in producer-side profits or pharmaceutical-industry surplus mechanically. Producer-side profits for type-$C$ firms rise only if the increase in qualified outsourcing demand dominates any offsetting increase in wages and manufacturing entry. Pharmaceutical-industry surplus rises only if gains from new original-drug products and more efficient organization outweigh producer-profit losses and switching costs.
\end{proposition}

\begin{proof}
The sign of the change in $\bar\Pi_C(M)$ depends on both the manufacturing-service price and the equilibrium cost side, including wages and entry. The sign of $\Surp(1)-\Surp(0)$ depends on all affected margins in equation \eqref{eq:industry_surplus}, not solely on the new-product term.
\end{proof}

\section{Calibration and estimation strategy}

We calibrate or estimate the model with moments from the pre- and post-MAH firm-level panel and innovation data. The transition matrix is one of the key sets of moments.

\subsection{Parameter blocks}

We group parameters into seven blocks.
\begin{enumerate}[leftmargin=2em]
    \item \textbf{Discounting and curvature:} $\beta$, $\eta$, and parameters of the manufacturing cost function.
    \item \textbf{Flow-payoff parameters for type $A$:} parameters in $\pi_A^G$, $\pi_A^{O,\mathrm{inc}}$, $\lambda_A(z)$, $R_A(z)$, and $f_A$.
    \item \textbf{Flow-payoff parameters for type $B$:} parameters in $R_B(z)$, $\lambda_B(z,p_m,M)$, $\chi_B$, $f_B$, and $\tau_M(M)$.
    \item \textbf{Flow-payoff parameters for type $C$:} parameters in $\pi_C^G$, $\pi_C^{O,\mathrm{inc}}$, $c(m,z;w)$, and $f_C$.
    \item \textbf{Switching costs:} the matrix $\{\kappa_{sj}(0),\kappa_{sj}(1)\}_{s,j\in\{A,B,C\},s\neq j}$.
    \item \textbf{State dynamics:} the transition kernels $Q_A,Q_B,Q_C$ and entrant distribution $G$.
    \item \textbf{Entry costs:} $c_{EA},c_{EB},c_{EC}$.
\end{enumerate}

\subsection{Moment selection}

We use the following moments:
\begin{enumerate}[leftmargin=2em]
    \item pre-MAH type shares $\mu_A,\mu_B,\mu_C$;
    \item the pre-MAH incumbent transition matrix $\mathbf P(0)$;
    \item the post-MAH incumbent transition matrix $\mathbf P(1)$;
    \item entry composition before and after MAH, $\mathbf e(0)$ and $\mathbf e(1)$;
    \item type-specific counts of original-drug applications, approvals, or closely related new-product measures before and after MAH;
    \item commercialization proxies for type-$B$ firms, such as entrusted-production mentions, commissioned-manufacturing text, and selling expenses;
    \item producer-side outcomes for type-$C$ firms, such as revenue growth, gross margin, and operating margin;
    \item generic-product sales or production moments for types $A$ and $C$, because the two-product structure gives generic cash flow an important role in organizational choice.
\end{enumerate}

\subsection{Moment-parameter mapping}

Table \ref{tab:calibration} summarizes the main moment-parameter mapping.

\begin{table}[htbp]
\centering
\caption{Illustrative calibration and estimation map}
\label{tab:calibration}
\begin{tabular}{p{0.28\textwidth}p{0.30\textwidth}p{0.32\textwidth}}
\toprule
Parameter block & Main moments & Interpretation \\
\midrule
$\beta$ & Standard annual calibration & Discounting. \\
$\eta,\chi_A,\chi_B$ & Dispersion of type-specific original-drug outcomes & Curvature and cost of original-drug research effort. \\
$f_A,f_B,f_C$ & Pre-MAH type shares and entry composition & Fixed organizational costs. \\
$\pi_A^G,\pi_C^G$ parameters & Generic sales, margins, or production moments by type & Generic cash-flow block in the two-medicine environment. \\
$\lambda_A,R_A,R_B$ parameters & Type-specific original-drug outcomes & Commercial value of successful original-drug ideas. \\
$\lambda_B(\cdot,0),\lambda_B(\cdot,1),$\newline$\tau_M(0),\tau_M(1)$ & Pre/post MAH type-$B$ commercialization proxies and original-drug outcomes & MAH-sensitive commercialization block. \\
$Q_A,Q_B,Q_C,G$ & Pre-MAH transition matrix and persistence moments & Capability dynamics and entrant heterogeneity. \\
$\kappa_{sj}(0)$ & Pre-MAH transition matrix $\mathbf P(0)$ & Baseline switching frictions. \\
$\kappa_{sj}(1)-\kappa_{sj}(0)$ & Post-MAH changes in the transition matrix & MAH-induced reorganization effect. \\
Manufacturing cost parameters & Type-$C$ revenue, margins, and output-related moments & Producer-side technology. \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Practical estimation}

A practical strategy is simulated method of moments or indirect inference. We discretize the capability state using a standard Markov approximation, solve the stationary equilibrium under $M=0$ and $M=1$, simulate the incumbent transition matrix, entry composition, type shares, new original-drug products, commercialization proxies, and producer-side moments, and choose parameters to minimize the weighted distance between simulated and empirical moments. The transition matrix and type-specific new-product moments are the key objects.

\section{Empirical mapping and data requirements}

The model is useful only if we can map its objects to observable data. The notes emphasize that the empirical classification may use four observable categories even though the model has three persistent types:
\begin{itemize}[leftmargin=2em]
    \item empirical R\&D type $\leftrightarrow$ model type $B$,
    \item empirical production type $\leftrightarrow$ model type $C$,
    \item empirical mixed type $\leftrightarrow$ model type $A$,
    \item empirical transitional type $\leftrightarrow$ an observed transitory state used to validate switching, not a fourth steady-state type.
\end{itemize}

We need at least the following data blocks.
\begin{enumerate}[leftmargin=2em]
    \item a firm-level panel that lets us classify firms into $A$, $B$, $C$, and transitional states;
    \item pre/post incumbent transition matrices across types;
    \item entry and exit by type, with entry separated from incumbent switching;
    \item original-drug application and approval outcomes or closely related new-product counts;
    \item generic-product sales or production measures by type;
    \item commercialization proxies such as entrusted-production mentions and commissioned-manufacturing text;
    \item producer-side outcomes for manufacturing specialists;
    \item policy timing and exposure measures that help distinguish MAH from the 2015 review-speed reform.
\end{enumerate}

\begin{table}[htbp]
\centering
\caption{Mapping model objects to empirical counterparts}
\label{tab:mapping}
\begin{tabular}{p{0.23\textwidth}p{0.32\textwidth}p{0.37\textwidth}}
\toprule
Model object & Empirical proxy & Comment \\
\midrule
$\mu_A,\mu_B,\mu_C$ & Number or share of mixed, R\&D, and production firms & Type masses by organization. \\
$\mathbf P(M)$ & Pre/post transition matrix across types & This is the key incumbent-reorganization object. \\
$\mathbf e(M)$ & Entry composition by first observed type & We must separate this from incumbent switching. \\
$\Inew(M)$ & Original-drug applications, approvals, or closely related new-product counts & This is the main policy outcome. \\
Generic cash-flow block & Generic sales, generic approvals, or generic-product production by type & Needed because the model has two medicines. \\
Commercialization block & Entrusted-production text, commissioned-manufacturing text, selling expenses & Indirect evidence on MAH-enabled commercialization. \\
$\bar\Pi_C(M)$ & Gross margin, operating margin, revenue growth for production firms & Needed for the producer-side equilibrium discussion. \\
\bottomrule
\end{tabular}
\end{table}

\section{What we changed relative to the one-product draft}

\begin{enumerate}[leftmargin=2em]
    \item We introduce \textbf{two medicine categories}, generic and original, because the policy question is about new original-drug products rather than total pharmaceutical output.
    \item We let \textbf{integrated firms and manufacturing firms produce both medicines}, while research-specialized firms generate only original-drug ideas.
    \item We encode the institutional point that \textbf{before MAH only firms that could both research and produce could independently commercialize new original drugs} by imposing $\lambda_B(z,p_m,0)=0$.
    \item We keep \textbf{all pairwise organizational switches} plus exit, because the incumbent transition matrix is one of the key empirical objects.
    \item We keep \textbf{beginning-of-period organizational choice} so that current-period commercialization possibilities are consistent with current-period organization.
    \item We focus the main outcome on \textbf{the number of new original-drug products} rather than on a generic innovation index.
\end{enumerate}

\section{References}

\begin{thebibliography}{99}

\bibitem[Acemoglu and Linn(2004)]{AcemogluLinn2004}
Acemoglu, Daron, and Joshua Linn. 2004.
\newblock Market Size in Innovation: Theory and Evidence from the Pharmaceutical Industry.
\newblock \emph{Quarterly Journal of Economics} 119(3): 1049--1090.

\bibitem[Aghion et~al.(2005)Aghion, Bloom, Blundell, Griffith, and Howitt]{AghionEtAl2005}
Aghion, Philippe, Nick Bloom, Richard Blundell, Rachel Griffith, and Peter Howitt. 2005.
\newblock Competition and Innovation: An Inverted-U Relationship.
\newblock \emph{Quarterly Journal of Economics} 120(2): 701--728.

\bibitem[Akcigit and Kerr(2018)]{AkcigitKerr2018}
Akcigit, Ufuk, and William R. Kerr. 2018.
\newblock Growth through Heterogeneous Innovations.
\newblock \emph{Journal of Political Economy} 126(4): 1374--1443.

\bibitem[Arora et~al.(2001)Arora, Fosfuri, and Gambardella]{AroraFosfuriGambardella2001}
Arora, Ashish, Andrea Fosfuri, and Alfonso Gambardella. 2001.
\newblock \emph{Markets for Technology: The Economics of Innovation and Corporate Strategy}.
\newblock Cambridge, MA: MIT Press.

\bibitem[Arora and Merges(2004)]{AroraMerges2004}
Arora, Ashish, and Robert P. Merges. 2004.
\newblock Specialized Supply Firms, Property Rights and Firm Boundaries.
\newblock \emph{Industrial and Corporate Change} 13(3): 451--475.

\bibitem[Arrow(1962)]{Arrow1962}
Arrow, Kenneth J. 1962.
\newblock Economic Welfare and the Allocation of Resources for Invention.
\newblock In \emph{The Rate and Direction of Inventive Activity: Economic and Social Factors}, 609--626.
\newblock Princeton, NJ: Princeton University Press.

\bibitem[Chandra et~al.(2026)Chandra, Kao, Miller, and Stern]{ChandraEtAl2026}
Chandra, Amitabh, Jennifer Kao, Kathleen L. Miller, and Ariel D. Stern. 2026.
\newblock Regulatory Incentives for Innovation: The FDA's Breakthrough Therapy Designation.
\newblock \emph{Review of Economics and Statistics} 108(2): 470--487.

\bibitem[Cunningham et~al.(2021)Cunningham, Ederer, and Ma]{CunninghamEdererMa2021}
Cunningham, Colleen, Florian Ederer, and Song Ma. 2021.
\newblock Killer Acquisitions.
\newblock \emph{Journal of Political Economy} 129(3): 649--702.

\bibitem[Ericson and Pakes(1995)]{EricsonPakes1995}
Ericson, Richard, and Ariel Pakes. 1995.
\newblock Markov-Perfect Industry Dynamics: A Framework for Empirical Work.
\newblock \emph{Review of Economic Studies} 62(1): 53--82.

\bibitem[Fons-Rosen et~al.(2026)Fons-Rosen, Roldan-Blanco, and Schmitz]{FonsRosenRoldanBlancoSchmitz2026}
Fons-Rosen, Christian, Pau Roldan-Blanco, and Tom Schmitz. 2026.
\newblock The Effects of Startup Acquisitions on Innovation and Economic Growth.
\newblock BSE Working Paper 1560.

\bibitem[Gans and Stern(2000)]{GansStern2000}
Gans, Joshua S., and Scott Stern. 2000.
\newblock Incumbency and R\&D Incentives: Licensing the Gale of Creative Destruction.
\newblock \emph{Journal of Economics \& Management Strategy} 9(4): 485--511.

\bibitem[Gans and Stern(2003)]{GansStern2003}
Gans, Joshua S., and Scott Stern. 2003.
\newblock The Product Market and the Market for ``Ideas'': Commercialization Strategies for Technology Entrepreneurs.
\newblock \emph{Research Policy} 32(2): 333--350.

\bibitem[Gans et~al.(2008)Gans, Hsu, and Stern]{GansHsuStern2008}
Gans, Joshua S., David H. Hsu, and Scott Stern. 2008.
\newblock The Impact of Uncertain Intellectual Property Rights on the Market for Ideas: Evidence from Patent Grant Delays.
\newblock \emph{Management Science} 54(5): 982--997.

\bibitem[Hopenhayn(1992)]{Hopenhayn1992}
Hopenhayn, Hugo A. 1992.
\newblock Entry, Exit, and Firm Dynamics in Long Run Equilibrium.
\newblock \emph{Econometrica} 60(5): 1127--1150.

\bibitem[Jia et~al.(2023)Jia, Ma, Yang, and Zhang]{JiaMaYangZhang2023}
Jia, Ruixue, Xiao Ma, Jianan Yang, and Yiran Zhang. 2023.
\newblock Improving Regulation for Innovation: Evidence from China's Pharmaceutical Industry.
\newblock NBER Working Paper 31976.

\bibitem[Jovanovic(1982)]{Jovanovic1982}
Jovanovic, Boyan. 1982.
\newblock Selection and the Evolution of Industry.
\newblock \emph{Econometrica} 50(3): 649--670.

\bibitem[Klette and Kortum(2004)]{KletteKortum2004}
Klette, Tor Jakob, and Samuel Kortum. 2004.
\newblock Innovating Firms and Aggregate Innovation.
\newblock \emph{Journal of Political Economy} 112(5): 986--1018.

\bibitem[Lakdawalla(2018)]{Lakdawalla2018}
Lakdawalla, Darius. 2018.
\newblock Economics of the Pharmaceutical Industry.
\newblock \emph{Journal of Economic Literature} 56(2): 397--449.

\bibitem[Luttmer(2007)]{Luttmer2007}
Luttmer, Erzo G. J. 2007.
\newblock Selection, Growth, and the Size Distribution of Firms.
\newblock \emph{Quarterly Journal of Economics} 122(3): 1103--1144.

\end{thebibliography}

\end{document}
